Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-11 latex/paper.tex
Summit description

\subsection{Experimental Platform}

\GB{Lawton, can you add a description of Summit?  use the recent SC submission as an example}

@@

\GB{Lawton, can you add these descriptions?}
\begin{itemize}
	\item synthetic (dense and sparse)
	\item HSI: DC and Aviris
	\item Doc-clustering: Reuters and PubMed
\end{itemize}

>>>>

\subsection{Experimental Platform}
All the experiments in this section were conducted on Summit. Summit is a supercomputer created by IBM for the Oak Ridge National Laboratory. 
There are approximately 4,600 nodes on Summit. Each node contains two IBM POWER9 processors on separate sockets with dual NVLINK bricks to facilitate a transfer rate of 
25 GB/s between the processors. Each node contains 512 GB of DDR4 memory for use by both processors. Each POWER9 processor utilizes 22 IBM SIMD Multi-Cores (SMCs), 
although one of these SMCs on each processor is dedicated to memory transfer and is therefore not available for computation. 
For node scaling experiments, all 42 available SMCs were utilized in each node so that every node computed with 42 separate MPI processes.
Additionally, every node also supports six NVIDIA Volta V100 accelerators but these were unused by our algorithm.

H2NMF uses the Armadillo library (version 9.900.1) for all matrix operations. 
In Armadillo, sparse matrices are stored in Compressed Sparse Column (CSC) format and dense matrices are stored in column-major ordering.
On Summit, we linked this version of Armadillo with OpenBLAS (version 0.3.9) and IBM's Spectrum MPI (version 10.3.1.2-20200121).

@@

\GB{Lawton, can you add these descriptions?}
\begin{itemize}

	\item synthetic (dense and sparse)
	\item HSI: DC and Aviris
	\item Doc-clustering: Reuters and PubMed
\end{itemize}
